### 2017-08-08 Paper01_EnthalpyAndCrystallization.tex
Results - Decon Onsets - Added a place holder gaussian fit equation

Numerical solutions were used to deconvolute the isochronic \acrshort{dsc} data so the various \Tx~ onsets could be accurately determined. This numerical fitting utilised a summation of skewed Gaussian curves to fit a target curve corresponding to the original data; as is a common method \cite{Ashour2010, Yamamoto2007, Spink2008, Spink2015, Schaffer2005}. The details of the fits for both the bulk and film are shown in Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon}.

The results of the deconvolution are presented in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film. Note \Tg~ and \Tx$_{1}$ are not obtained from the original raw data, not the deconvolution.

>>>>

Numerical solutions were used to deconvolute the isochronic \acrshort{dsc} data so the various \Tx~ onsets could be accurately determined. This numerical fitting utilised a summation of skewed Gaussian curves to fit a target curve corresponding to the original data; as is a common method \cite{Ashour2010, Yamamoto2007, Spink2008, Spink2015, Schaffer2005}. This fitting summation takes the form of Equation \ref{equ:GaussianSummation} \todo{this is non-skewed form. It is a place holder}.

\begin{equation}
	f(x) = \sum_{n=i}^{n} h_{i}~ e^-{\bigg(\frac{(x-T_{i})^2}{(2c_{j})^2}\bigg)}
	\label{equ:GaussianSummation}
\end{equation}

Where $h$ is the enthalpy peak intensity, $T$ is the temperature at the enthalpy peak centre, and $c$ is the Gaussian RMS width.

The final solutions of this fitting for both the bulk and film are shown in Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon}.

The results of the deconvolution are presented in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film. Note \Tg~ and \Tx$_{1}$ are obtained from the original raw data, not the deconvolution.
